High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-08-23 notebooks/prototyping.qmd
that's done for now

```{julia}
# Model parameters:
epochs = 100
batch_size = minimum([Int(round(n_obs/10)), 128])
n_hidden = 16
activation = Flux.swish
builder = MLJFlux.MLP(
    hidden=(n_hidden, n_hidden, n_hidden), 
    σ=Flux.swish
)
n_ens = 5                                   # number of models in ensemble
_loss = Flux.Losses.crossentropy       # loss function
_finaliser = Flux.softmax                   # finaliser function
```

@@

```{julia}
# Joint Energy Model:
model = JointEnergyClassifier(
    sampler;
    builder=builder,
    epochs=epochs,
    batch_size=batch_size,
    finaliser=_finaliser,
    loss=_loss,
    jem_training_params=(
        α=α,verbosity=10,
    ),
    sampling_steps=30,
)
```

@@

X = X isa Matrix ? X : Float32.(permutedims(matrix(X)))
factual_label =  levels(labels)[1]
x_factual = reshape(X[:,rand(findall(predict_label(M, counterfactual_data).==factual_label))],input_dim,1)
target =  levels(labels)[2]
factual = predict_label(M, counterfactual_data, x_factual)[1]

>>>>

```{julia}
# Model parameters:
epochs = 100
bs = minimum([Int(round(n_obs/10)), 128])
n_hidden = 16
activation = Flux.swish
builder = MLJFlux.MLP(
    hidden=(n_hidden, n_hidden, n_hidden), 
    σ=Flux.swish
)
n_ens = 5                                   # number of models in ensemble
_loss = Flux.Losses.crossentropy       # loss function
_finaliser = Flux.softmax                   # finaliser function
```

@@

```{julia}
# Joint Energy Model:
model = JointEnergyClassifier(
    sampler;
    builder=builder,
    epochs=epochs,
    batch_size=bs,
    finaliser=_finaliser,
    loss=_loss,
    jem_training_params=(
        α=α,verbosity=10,
    ),
    sampling_steps=30,
)
```

@@

X = X isa Matrix ? X : Float32.(permutedims(matrix(X)))
factual_label =  levels(labels)[2]
x_factual = reshape(X[:,rand(findall(predict_label(M, counterfactual_data).==factual_label))],input_dim,1)
target =  levels(labels)[1]
factual = predict_label(M, counterfactual_data, x_factual)[1]
